---
title: "Horror Movie Quality vs. Budget"
description: For a film distribution company, are measures of audience engagement and approval on IMDb good indicators of how much revenue a potential film will earn? In this study, Over the summer, I interned for a film distribution company whose purpose is to aquire films to be distributed on streaming platforms like Pluto TV, Amazon Video, and Peacock. The biggest concern was whether an aquired film will be lucrative. It has to be good enough to interest viewers; the more viewers the more revenue brought in to the company. Therefore, in this study, I aim to use the movie database platform IMDb to find out if it can be used to accurately analyze a film's earning potential before deciding to buy the rights. IMDb has two statistics that I'm interested in for measuring audience engagement and approval: Votes and Rating. Votes indicates how many people "like" a film, while Rating is more two sided by indicating both whether viewers tend to like or dislike a film. Votes are better at gaging audience engagement than approval: higher-grossing films tend to get more Votes because films with the most viewers are engaged with the most on IMDb. On the other hand, Ratings do not reflect how many viewers interact with a film on the platform. My hypothesis is that more votes correlates with more gross revenue earned, which would make IMDb Votes a good measure of a film's money-making potential. On the contrary, I predict that IMDb Rating has no correlation with gross revenue, because even films that are considered "bad," as in, low quality, cheesy, etc. can earn a lot of money and viewers (for example, Snakes on a Plane and Sharknado). My explanatory variables are IMDb Votes and Rating. My outcome variable is Gross Revenue, which measures the gross revenue of a film upon release. 
  A new article created using the Distill format.
author:
  - name: Alex Ankai 
date: 12/13/23
output: distill::distill_article
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
distill::distill_article
```

Distill is a publication format for scientific and technical writing, native to the web. 

Learn more about using Distill for R Markdown at <https://rstudio.github.io/distill>.


```{r}
library(tidyverse)
library(stringr)


imdb <- read_csv("imdbdata.csv")
imdb

imdb <- imdb |>
  rename(rating = `Rating`) |>
  rename(title = `Movie Title`) |>
  rename(year = `Movie Year`) |>
  rename(runtime = Runtime) |>
  rename(genre = Genre) |>
  rename(director = Director) |>
  rename(votes = Votes) |>
  rename(gross = Gross) |>
  filter(year >= 2000)

imdb
  

imdb <- imdb |>
  mutate(gross = as.character(gross)) |>
  mutate(gross = as.numeric(str_extract(gross, "\\d+\\.*\\d*")))

```


## Audience Engagement: Votes

```{r}

imdb |>
  ggplot(aes(x = votes, y = gross, na.rm = TRUE)) +
  geom_point() + geom_smooth() +
  scale_x_log10() +
  labs(x = "Votes",
       y = "Gross Revenue (Millions of Dollars)",
       title = "IMDb Votes and Gross Revenue")
  

```

The scatterplot is consistent with my hypothesis that more IMDb Votes correlates to higher gross revenue. 



## Audience Approval: Rating

```{r}

imdb |>
  ggplot(aes(x = rating, y = gross, na.rm = TRUE)) +
  geom_col() + 
  labs(x = "Rating",
       y = "Gross Revenue (Millions of Dollars)",
       title = "IMDb Rating and Gross Revenue")

```

With some exeptions, the data seems to be skewed left, evidencing that contrary to my hypothesis, a higher IMDb Rating, and thus, higher audience approval, does point to more gross revenue, where I had hypothesized that there was no correlation. And so a higher number of Votes does seem to be a good indicator of increased financial viability of potential horror films. Interestingly, there additionally are films with high ratings and very low gross revenue.


## Regression

```{r}

reg_imdb <- lm(gross ~ votes + rating, data = imdb)
summary(reg_imdb)

```

The coefficient is not statisctically significant at the 0.05 level, and I don't believe the coefficient represents a causal effect.