---
title: "Horror Movie Quality vs. Budget"
description: If you're a film distribution company looking to own horror content that will make the most money, I will see if IMDb audience engagement and approval translates to money making ability, and if IMDb stats like votes and ratings are good inidcators of how much money a movie makes.
  A new article created using the Distill format.
author:
  - name: Alex Ankai 
date: 12/13/23
output: distill::distill_article
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
distill::distill_article
```

Distill is a publication format for scientific and technical writing, native to the web. 

Learn more about using Distill for R Markdown at <https://rstudio.github.io/distill>.


```{r}
library(tidyverse)
library(stringr)


imdb <- read_csv("imdbdata.csv")
imdb

imdb <- imdb |>
  rename(rating = `Rating`) |>
  rename(title = `Movie Title`) |>
  rename(year = `Movie Year`) |>
  rename(runtime = Runtime) |>
  rename(genre = Genre) |>
  rename(director = Director) |>
  rename(votes = Votes) |>
  rename(gross = Gross) |>
  filter(year >= 2000)

imdb
  

imdb <- imdb |>
  mutate(gross = as.character(gross)) |>
  mutate(gross = as.numeric(str_extract(gross, "\\d+\\.*\\d*")))

```


## Audience Engagement: Votes

```{r}

imdb |>
  ggplot(aes(x = votes, y = gross, na.rm = TRUE)) +
  geom_point() + geom_smooth() +
  scale_x_log10() +
  labs(x = "Votes",
       y = "Gross Revenue (Millions of Dollars)",
       title = "IMDb Votes and Gross Revenue")
  

```

The scatterplot is consistent with my hypothesis that more IMDb Votes correlates to higher gross revenue. 



## Audience Approval: Rating

```{r}

imdb |>
  ggplot(aes(x = rating, y = gross, na.rm = TRUE)) +
  geom_col() + 
  labs(x = "Rating",
       y = "Gross Revenue (Millions of Dollars)",
       title = "IMDb Rating and Gross Revenue")

```

With some exeptions, the data seems to be skewed left, evidencing that contrary to my hypothesis, a higher IMDb Rating, and thus, higher audience approval, does point to more gross revenue, where I had hypothesized that there was no correlation. And so a higher number of Votes does seem to be a good indicator of increased financial viability of potential horror films. Interestingly, there additionally are films with high ratings and very low gross revenue.


## Regression

```{r}

reg_imdb <- lm(gross ~ votes + rating, data = imdb)
summary(reg_imdb)

```

The coefficient is not statisctically significant at the 0.05 level, and I don't believe the coefficient represents a causal effect.